---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## Aucklander's Fruit Consumption Preferences

This report presents a dynamic analysis of survey data collected on fruit purchasing and consumption habits in Auckland. The survey includes responses about how often participants buy fruit, how much they are willing to spend, their favourite fruits, and their perception of fruit prices.

The dataset was collected via an online Google Form and reflects opinions and behaviours from a range of respondents.


```{r}
library(tidyverse)

logged_data <- read_csv("Eating Fruit Survey.csv")



latest_data <- logged_data %>%
  rename(
    timestamp = `Timestamp`,
    buy_freq = `How often do you buy fruit to eat?`,
    spend_affordable = `How much do you think is affordable to spend on fruit weekly?`,
    shop_location = `Where do you usually buy fruit from?`,
    fav_fruit = `What's you favourite fruit?`,
    price_rating = `How do you think the fruit price in Auckland`
  )


mean_spend <- mean(latest_data$spend_affordable, na.rm = TRUE)
print(paste("Average Acceptable Cost (per week):", mean_spend))


max_price_rating <- max(latest_data$price_rating, na.rm = TRUE)
print(paste("The maximum value of fruit price rating:", max_price_rating))


ggplot(latest_data, aes(x = buy_freq)) +
  geom_bar(fill = "steelblue") +
  labs(title = "Frequency of Buying Fruit", x = "Frequency", y = "Number of Respondents") +
  theme_minimal()

ggplot(latest_data, aes(x = fav_fruit)) +
  geom_bar(fill = "darkorange") +
  labs(title = "Favourite Fruit Choices", x = "Fruit", y = "Number of Respondents") +
  theme_minimal()

```

